---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BDEEPdbZillow)
```

get_from_db_fips

This function gets a data.frame including all data from the given fips. Use previous function.
Parameters:
    fips          A vector of fips
    columns       A vector of column names to export. Default to all columns (i.e. "*").
    database_name A string indicating the database name
    host_ip       A string indicating the ip address of the database VM
    append        If append is true, return a single data.frame with rows appended, otherwise a
                     list of data.frames from each state.
                
```{r}
data <- get_from_db_fips("10001")
head(data)
data <- get_from_db_fips(c("01001","17019"))
head(data)
```
                     
get_from_db_state

This function gets a list of data.frames from the database, according to the given states (through abbreviation).
Parameters:
    states_abbr   A vector of states abbreviation
    columns       A vector of column names to export. Default to all columns (i.e. "*").
    max_num_recs  An integer indicating the maximum number of records to select, -1 indicating all (by default)
    database_name A string indicating the database name
    host_ip       A string indicating the ip address of the database VM
    append        If append is true, return a single data.frame with rows appended, otherwise a list of data.frames from each state.
  
```{r}
data <- get_from_db_state("sd")
head(data)
data <- get_from_db_state(c("sD","Ne"), append=FALSE)
head(data)
data <- get_from_db_state("ca",columns=c("rowid","transid"))
head(data)
data <- get_from_db_state("sd",max_num_recs=100)
```

get_from_db_state_county

This function gets a data.frame including all data from the given state abbr. and county.

Parameters:
    state_county  A data.frame with two columns representing state and county name
    columns       A vector of column names to export. Default to all columns (i.e. "*").
    database_name A string indicating the database name
    host_ip       A string indicating the ip address of the database VM
    append        If append is true, return a single data.frame with rows appended, otherwise a list of data.frames from each state.
    
```{r}
table <- get_state_county("01001")[, c("state","county")]
data <- get_from_db_state_county(table)
head(data)
```

get_from_db_usr

This function gets from database according to a user-specified query.

Parameters:
    query         A string specifying the query sent to database
    database_name A string indicating the database name
    host_ip       A string indicating the ip address of the database VM
  
```{r}
get_from_db_usr("SELECT loadid FROM hedonics_new.sd_hedonics_new")
```